---
title: "writing_functions"
author: "Wenshan Qu (wq2160)"
date: "11/4/2021"
output: html_document
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Z scores

```{r}
x_vec = rnorm(25, mean = 5, sd = 4)

(x_vec - mean(x_vec)) / sd(x_vec)

## Construct a function
z_score = function(x) {
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}
## Test our created function
z_score(x = x_vec)

## Test 2
y_vec = rnorm(40, mean = 12, sd = .3)

z_score(x = y_vec) ## More safe to use `x = `
```


How great is this?

```{r, error = TRUE}
z_score(3)

z_score(mtcars)

z_score(x = y_vec)
```



Modify our function: 

```{r}
z_score = function(x) {
  
  if(!is.numeric(x)) {
    stop("x need to be numeric")
  }
  
  if(length(x) < 3) {
    stop("x should have at least 3 numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}
```

Test：

```{r, error=TRUE}
z_score(3)

z_score(mtcars)

z_score(x = y_vec)
```

How to output 2 results.

```{r}
mean_and_sd = function(x) {
  
  if(!is.numeric(x)) {
    stop("x need to be numeric")
  }
  
  if(length(x) < 3) {
    stop("x should have at least 3 numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  output_df = 
    tibble(
      mean = mean_x,
      sd = sd_x
    )
  
  return(output_df)
  
}

mean_and_sd(x_vec)
mean_and_sd(x = y_vec)
```

you can use `rm(x)` to remove a `x` to ensure this function is reproducible.


## Different sample sizes, means, sds

```{r}
sim_data = 
  tibble(
    x = rnorm(30, mean = 2, sd = 3)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )


```


Let's write a function that simulates data, computes the mean and sd.

```{r}
## We want n, true mean and true sigma input
sim_mean_sd = function(n, mu, sigma) {
  
  ## do checks on inputs

sim_data = 
  tibble(
    x = rnorm(n, mean = mu, sd = sigma)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
  
}

## R will default seen your data as in order. But using `n, mu, sigma` to specify them is great.
sim_mean_sd(n = 30, mu = 4, sigma = 3)

```

Note: you need to pay attention on whether there is a same variable outside the function, bcs this will make your function useless. You should ensure that this function did not include any variable names that appears before.

```{r}

```


